\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{setspace}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ben Brown} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(484) 788-3226 \\ Emmaus, PA} 
\address{
\href{brown.ben.2019@gmail.com}{brown.ben.2019@gmail.com} \\
\href{https://linkedin.com/in/bendoesai}{linkedin.com/in/bendoesai}}  
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}
% change to professional summary, sell experience
{Passionately motivated engineer and researcher with 2+ years experience 
solving complex problems across diverse fields.
Seeking full-time,
 cross-disciplinary work combining programming, engineering, 
 and ethics in a research setting. 
 {\bf \\Available Immediately}
}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BS Electrical Engineering}, Rochester Institute of Technology \hfill {Earned 2024}\\
{\bf Applied Statistics Immersion}, Rochester Institute of Technology \hfill {Earned 2024}\\
{\bf GPA:} 3.08


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Software & Python, 
Pytorch, 
TensorFlow, 
C/C++,
Assembly (MSP430),  
Git tools, 
\LaTeX
\\
Hardware & 
Verilog/VHDL, 
Embedded Systems, 
Electrical Lab Tools,
Circuit Analysis (AC/DC)


\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
\textbf{Research Assistant} \textbar\ \textit{Cybersecurity} \hfill Aug 2023 - Dec 2023, May 2024-Present\\
DeFake Project \hfill \textit{Rochester, NY}
\begin{itemize}
\itemsep-3pt {}
    \item Used PyTorch to write a modular, scalable framework for variable-scale analysis, with a publication target of a November 2024 conference.
    \item Wrote memory-efficient code extending Adversarial Robustness Toolbox to attack various models.
    \item Operated Ubuntu command line and VSCode to collect data and identified several vulnerabilities in common deepfake detection architectures.
    \item Participated in team reading groups about Artificial Intelligence and Cybersecurity.
\end{itemize}

\textbf{Team Lead} \textbar\ \textit{Agriculture Technology} \hfill August 2023 - May 2024\\
RIT Multidisciplinary Senior Design \hfill \textit{Rochester, NY}
\begin{itemize}
\itemsep-3pt {}
    \item Prototyped support circuitry for Fabry-perot spectral sensor using LTspice simulations and schematic capture.
    \item Served as primary contact between customer and team by scheduling design reviews and sending weekly updates.
    \item Designed conference posters and drafted a detailed technical report using Microsoft Office.
    \item Showcased final results at Imagine RIT 2024 and CEIS Symposium
\end{itemize}

\textbf{Electrical Intern} \textbar\ \textit{Defense} \hfill Jan 2023 - Aug 2023\\
L3Harris Technologies \hfill \textit{Rochester, NY}
\begin{itemize}
\itemsep-3pt {}
    \item Wrote Python to automate hardware checks of VHF radios, increasing testing efficiency by 57\%.
    \item Communicated with embedded linux environment via serial port to log errors for more meaningful verification.
    \item Operated oscilloscopes, multimeters, and soldering to debug and repair failing units.
\end{itemize}

\textbf{Electrical Intern (ML/AI)} \textbar\ \textit{Titanium Production} \hfill Jan 2022 - Aug 2022\\
TIMET Morgantown \hfill \textit{Morgantown, PA}
\begin{itemize}
    \itemsep-3pt {}
    \item Used SQL database to analyze historical data and implement innovation to save the company seven figures annually.
    \item Deployed time series prediction technologies and python tools (NumPy, Pandas, Scikit-learn) to estimate chemical profile of furnace contents and ensure melt quality.
    \item Advocated for ethical implementation of technological tools to prevent reckless worker displacement.
    \item Designed custom genetic algorithm to optimize XGBoost hyperparameters in production use.
\end{itemize}

\end{rSection} 



\end{document}